### 2025-08-03 conteudo/introduction/intro.tex
update the points for abstract and intro

This research presents ArKanjo, a command-line tool designed to detect and analyze function-level 
duplications in the Linux kernel. Released under the MIT license, ArKanjo uses a two-stage 
architecture with a Preprocessor and a Query Responder. This design separates the heavy 
computational analysis from the fast querying of duplication results, making it effective for 
large codebases. We validated the tool by comparing its results with the BigCloneBench
dataset~\citep{bigclonebench} and by conducting an empirical analysis on a randomly selected set of 
files from the AMD Display driver.

>>>>

This work presents an approach to address the code duplication issue in the Linux kernel; to 
support this approach, we developed ArKanjo, a command-line tool designed to detect and analyze 
function-level duplications. Released under the MIT license, ArKanjo uses a two-stage 
architecture with a Preprocessor and a Query Responder. This design separates the heavy 
computational analysis from the fast querying of duplication results, making it effective for 
large codebases. We validated the tool by comparing its results with the BigCloneBench
dataset~\citep{bigclonebench} and by conducting an empirical analysis on a randomly selected set of 
files from the AMD Display driver.
